## Cylinders for a valve DN  `r df$dn.valve`

### Template for drilling the cylinder

Production Details:

-   **Valve Diameter:** `r df$dn.valve` $mm$
-   **Cylinder External Diameter:** `r df$dn.ext` $mm$
-   **Thickness:** `r df$thickness` $mm$
-   **Material:** 304 Stainless Steel
-   **Metal Sheet Length:** `r df$length` $mm$
-   **Metal Sheet Width:** `r round(df$circumf,1)` $mm$
-   **Number of rails/cylinder areas:** `r df$rail.n`
-   **Rail width:** `r df$rail.width` ° $degrees$
-   **Net Area:** `r format(df$area.net, digits=2, big.mark="," , nsmall=2)` $mm^2$
-   **Net Area relative to the valve area:** `r sprintf("%.1f %%", 100*df$area.relative)`

```{r echo=FALSE}
  p1 <- plot.area.cylinder(dim.cylinder,dn, dist.type = 90)
  p2 <- plot.area.cylinder(dim.cylinder,dn, dist.type = 45)
  
  grid.arrange(p1, p2, ncol=1, nrow=2 ,
               top =  paste0("Template for perforations of the cylinder for Valve DN-", dn, " mm "),
               bottom = textGrob( "Dr.Trujillo", gp = gpar(fontface = 3, fontsize = 9),
                                  hjust = 1, x = 1 ))
```


### Mould for the area of perforation

```{r  echo=FALSE}
  total.orifices45      <- (df$h.orifices*df$v.orifices) + (df$h.orifices-df$rail.n)*(df$v.orifices - 1)
  horizontal.orifices45 <- 2 * df$h.orifices - 1
  vertical.orifices45   <- 2 * df$v.orifices - 1
```


Details:

|                                           |  Level round hole 90° (Straight Line)                              | Staggered round hole 45°                                          | 
|-------------------------------------------|-------------------------------------------------------------------:|------------------------------------------------------------------:|
| **Diameter of the orifices:**             | `r df$dn.h90` $mm$                                                 | `r df$dn.h45` $mm$                                                |
| **Total number of orifices:**             | `r df$h.orifices*df$v.orifices` $units$                            | `r total.orifices45` $units$                                      |
| **Horizontal Number of orifices:**        | `r df$h.orifices/df$rail.n`     $units$                            | `r horizontal.orifices45` $units$                                 |
| **Vertical Number of orifices:**          | `r df$v.orifices`               $units$                            | `r vertical.orifices45` $units$                                   |
| **Total flow area:**                      | `r format(df$area.h90, digits=2, big.mark="," , nsmall=2)` $mm^2$  | `r format(df$area.h45, digits=2, big.mark="," , nsmall=2)` $mm^2$ |
| **Flow area relative to the valve area:** | `r sprintf("%.1f %%", 100*df$area.hole.valve90)`                   | `r sprintf("%.1f %%", 100*df$area.hole.valve45)`                  |


```{r echo=FALSE, out.width = '100%'}
  # p1 <- plot.orifices(dim.cylinder, dn, dist.type = 90)
  # p2 <- plot.orifices(dim.cylinder, dn, dist.type = 45)
  # p3 <- plot.slott(df, dn, dist.type = 90)
  # 
  # grid.arrange(p1, p2, p3, ncol=1, nrow=3 ,
  #              top =  paste0("Template for perforations area of the cylinder for Valve DN-", dn, " mm "),
  #              bottom = textGrob( "Dr.Trujillo", gp = gpar(fontface = 3, fontsize = 9),
  #                                 hjust = 1, x = 1 ))  
```

```{r echo=FALSE, out.width = '200%'}
  plot.orifices(dim.cylinder, dn, dist.type = 90)
```

```{r echo=FALSE, out.width = '200%'}
  plot.orifices(dim.cylinder, dn, dist.type = 45)
```

```{r echo=FALSE, out.width = '200%'}
  plot.slott(df, dn, dist.type = 90)
```